Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-03-04 size_differentiated_export.tex
Updates from Overleaf

>>>>

\begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum})}
	\label{fig: biomass_export}
\end{figure}
